Tropical Andes montane and lowland forest bird and mammal species GBIF

### 2023-07-25 code/L0/L0_TropicalAndes_frugivores_GBIF.Rmd
add additional summary and species list code

# Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropAndes_GBIF_frugivore_occ.csv") 
write.csv(d, file = TropicalAndes_GBIF_path)
```

>>>>

```{r}
print("The number of records is")
nrow(d)
print("The number of species is")
length(unique(d$species))
print("The number of families is")
length(unique(d$family))
```

# Extract species list
```{r}
GBIF_occ_SpeciesList <- unique(d$species)
```

# Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropAndes_GBIF_frugivore_occ.csv") 
write.csv(d, file = TropicalAndes_GBIF_path)
TropicalAndes_GBIF_species_path <- file.path(output_path,"TropAndes_GBIF_frugivore_occ_species.csv") 
write.csv(GBIF_occ_SpeciesList, file = TropicalAndes_GBIF_path)
```
